Towards Cloud Bursting for Extreme Scale Supercomputers

### 2014-06-18 paper/paper.tex
0619

\begin{figure}[tb]
	\centering
%	\includegraphics[width=6cm]{overview}
	\caption{overall illustrate of I/O Bursting Buffer Architecture}
	\label{overview}
\end{figure}

@@

\begin{figure}[tb]
	\centering
%	\includegraphics[width=8cm]{reading}
	\caption{data reading operation}
	\label{reading}
\end{figure}

\begin{figure}[tb]
	\centering
%	\includegraphics[width=8cm]{writing}
	\caption{data writing operation}
	\label{writing}
\end{figure}

@@

\begin{figure}[tb]
	\centering
%	\includegraphics
	\caption{definition}
	\label{definition}
\end{figure}

Throughput-based Model and Cost-based Model will be described in this section.
All definitions used are described in Fig.~\ref{definition}:

@@

\section{Evaluation}
In this section, a simulation will be introduced based on data taking from several benchmarks on both TSUBAME and AMAZON EC2.

>>>>

\begin{figure}[tb]
	\centering
	\includegraphics[width=6cm]{overview}
	\caption{overall illustrate of I/O Bursting Buffer Architecture}
	\label{overview}
\end{figure}

@@

\begin{figure}[tb]
	\centering
	\includegraphics[width=8cm]{reading}
	\caption{data reading operation}
	\label{reading}
\end{figure}

\begin{figure}[tb]
	\centering
	\includegraphics[width=8cm]{writing}
	\caption{data writing operation}
	\label{writing}
\end{figure}

@@

%\begin{figure}[tb]
%	\centering
%	\includegraphics
%	\caption{definition}
%	\label{definition}
%\end{figure}

Throughput-based Model and Cost-based Model will be described in this section.
All definitions used are described in Fig.~\ref{overview}:

@@

\section{Evaluation}
\begin{figure}[tb]
	\centering
	\includegraphics[width=8cm]{ThroughputAMAZONTSUBAME}
	\caption{Throughput between AMAZON and TSUBAME}
	\label{Throughput between AMAZON and TSUBAME}
\end{figure}

In this section, a simulation will be introduced based on data taking from several benchmarks on both TSUBAME and AMAZON EC2.
